### 2021-03-05 paper2/appendix.tex
Use include instead of import
This has the advantage that I can compile one chapter at a time.

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.85\textwidth]{./Figures/nosinn_adult_multiplot_all_landscape_diff.pdf}
  \caption{
      Results for the \textsc{Adult} dataset.
      The $x$-axis corresponds to the difference in positive rates.
      An ideal result would occupy the \textsc{top-left}.
  }%
  \label{fig:big-adult-chart}
\end{figure}
\begin{figure}[htb]
    \centering
    \includegraphics[width=0.7\textwidth]{Figures/celeba_multi_s.pdf}
    \caption{
        For \emph{hair color}, $s$ takes on the values Blond, Brown and Black.
        For \emph{age+gender}, $s$ takes on the values Young/Female, Young/Male, Old/Female and Old/Male.
    }%
    \label{fig:multi-s}
\end{figure}

\paragraph{Multinomial sensitive attributes.}
In addition to binary sensitive attribute $s$,
we also investigate multinomial $s$ in the CelebA dataset.
First, we do experiments with hair color, where $s$ has three possible values:
blond hair, brown hair and black hair.
The other experiment is with a combination of age and gender,
where $s$ has four possible values, each of which is a combination of a gender and an age:
Young/Female, Young/Male, Old/Female and Old/Male.
To evaluate the fairness for multinomial $s$, we use the Hirschfeld-Gebelein-R\'enyi Maximum Correlation Coefficient (HGR) \citep{mary2019fairness} that is defined on the domain $[0, 1]$ and gives $\text{HGR}(Y,S)=0$ iff $Y \perp S$
and 1 if there is a deterministic function to map between them.
Results can be found in figure~\ref{fig:multi-s}.\\

@@

% \newpage
\begin{figure*}[tb]
  \centering
  \subfloat[Original images.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{./Images/celeba/vae_x_original.png}}%
      \label{fig:cvae_celeba_original_x}
  }
  \hfill
  \subfloat[$\bm{x}_u$ null-samples generated by the cVAE model.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{./Images/celeba/vae_recon_y.png}}%
      \label{fig:cvae_celeba_recon_y}
  }
  \hfill
  \subfloat[$\bm{x}_b$ null-samples generated by the cVAE model.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{./Images/celeba/vae_recon_s.png}}%
      \label{fig:cvae_celeba_recon_s}
  }
  \caption{
    CelebA null-samples learned by our cVAE model, with gender as the sensitive attribute.
    (a) The original, untransformed samples from the CelebA dataset
    (b) Reconstructions using only information unrelated to $s$.
    (c) Reconstruction using only information related to $\neg s$.
    The model learns to disentangle gender from the non-gender related information. Compared with the cFlow model, there is a severe degradation in reconstruction quality due to the model trying to simultaneously satisfy conflicting objectives.
    % Attributes such as \emph{makeup} and \emph{hair length} are also often modified in the process due to inherent correlations between them and the sensitive attribute, which the intepretability of our representations allows us to easily identify.
  }\label{fig:celeba_vae}
\end{figure*}

\begin{figure*}[tb]
  \centering
  \subfloat[Original images.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{./Images/celeba/cflow_original_x_suppmat.png}}%
      \label{fig:cflow_celeba_original_x_suppmat}
  }
  \hfill
  \subfloat[$\bm{x}_u$ null-samples generated by the cFlow model.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{./Images/celeba/cflow_xd_suppmat.png}}%
      \label{fig:cflow_celeba_recon_y_suppmt}
  }
  \hfill
  \subfloat[$\mathbf{x}_b$ null-samples generated by the cFlow model.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{./Images/celeba/cflow_xb_suppmat.png}}%
      \label{fig:cflow_celeba_recon_s_suppmat}
  }
  \caption{
    CelebA null-samples learned by our cFlow model, with gender as the sensitive attribute.
    (a) The original, untransformed samples from the CelebA dataset
    (b) Reconstructions using only information unrelated to $s$.
    (c) Reconstruction using only information related to $\neg s$.
    The model learns to disentangle gender from the non-gender related information.
    Attributes such as \emph{makeup} and \emph{hair length} are also often modified in the process (prime examples framed with red) due to inherent correlations between them and the sensitive attribute, which the interpretability of our representations allows us to easily identify.
  }\label{fig:celeba_cflow_suppmat}
\end{figure*}

@@

The results for the range of $\sigma$ values are shown in fig.~\ref{fig:cmnist-transfer}. Unsurprisingly, the performance of both models suffers when the representative and test sets do not completely correspond. However, the cFlow model consistently outperforms the cVAE model, with the gap increasing as the bias decreases.
Although some colour information is retained in the cFlow null-samples, symptomatic of an imperfect transfer, semantic information is almost entirely retained as well.
Conversely, the cVAE is very much flawed in this respect; as can be seen in the bottom row of fig.~\ref{fig:cmnist-transfer}, for some samples, semantic information is degraded to the point of the digit's identity being altered. As a result of this semantic degradation, the performance of the downstream classifier is curtailed by the noisiness of the digit's identity and is relatively unchanging across $\sigma$-values, in contrast to the monotonic improvement of that achieved on the cFlow null-samples.
% \begin{figure}
%   \includegraphics[width=0.6\textwidth]{./Figures/nosinn_cmnist_transfer.pdf}
%   \caption{
%      Results for transfer learning experiments on cMNIST.
%   }%
%   \label{fig:cmnist-transfer}
% \end{figure}

\begin{figure*}[htb]
  \centering
  \subfloat[Performance on cMNIST test data after pre-training on the mixed NIST dataset.]{
      \scalebox{0.6}{\includegraphics[width=\textwidth]{./Figures/nosinn_cmnist_transfer.pdf}} \label{fig:cmnist-transfer}
  }
  %---
  \vspace{10pt}

  \subfloat[Test data input to the cFlow model.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{./Images/cmnist/cflow_tl_original.png}}%
      \label{fig:cflow_tl_original}
  }
  ~~~
%   \hfill
  \subfloat[$\bm{x}_u$ null-samples generated by the cFlow model.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{./Images/cmnist/cflow_tl_xd.png}}%
      \label{fig:cflow_tl_xd}
  }

    \subfloat[Test data input to the cVAE model.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{./Images/cmnist/cvae_tl_original.png}}%
      \label{fig:cvae_tl_original}
  }
  ~~~
%   \hfill
  \subfloat[$\bm{x}_u$ null-samples generated by the cVAE model.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{./Images/cmnist/cvae_tl_xd.png}}%
      \label{fig:cvae_tl_xd}
  }
  \caption{
    Results for the transfer learning experiments in which the representative set consists of colourised samples from EMNIST, KMNIST, and FashionMNIST, while the downstream dataset remains as cMNIST. (a) Quantitative results for different $\sigma$-values. (b-c) Qualitative results for the cFlow model.
    (d-e) Qualitative results for the cVAE model. The qualitative results provide comparisons of the images before (left) and after (right) null-sampling. Note that for some of the cVAE samples, the clarity of the digits has clearly changed due to null-sampling, serving as an explanation for the non-increasing downstream performance.
  }%
  \label{fig:cmnist-transfer-all}

>>>>

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.85\textwidth]{paper2/Figures/nosinn_adult_multiplot_all_landscape_diff.pdf}
  \caption{
      Results for the \textsc{Adult} dataset.
      The $x$-axis corresponds to the difference in positive rates.
      An ideal result would occupy the \textsc{top-left}.
  }%
  \label{fig:big-adult-chart}
\end{figure}
\begin{figure}[htb]
    \centering
    \includegraphics[width=0.7\textwidth]{paper2/Figures/celeba_multi_s.pdf}
    \caption{
        For \emph{hair colour}, $s$ takes on the values Blond, Brown and Black.
        For \emph{age+gender}, $s$ takes on the values Young/Female, Young/Male, Old/Female and Old/Male.
    }%
    \label{fig:multi-s}
\end{figure}

\paragraph{Multinomial sensitive attributes.}
In addition to binary sensitive attribute $s$,
we also investigate multinomial $s$ in the CelebA dataset.
First, we do experiments with hair colour, where $s$ has three possible values:
blond hair, brown hair and black hair.
The other experiment is with a combination of age and gender,
where $s$ has four possible values, each of which is a combination of a gender and an age:
Young/Female, Young/Male, Old/Female and Old/Male.
To evaluate the fairness for multinomial $s$, we use the Hirschfeld-Gebelein-R\'enyi Maximum Correlation Coefficient (HGR) \citep{mary2019fairness} that is defined on the domain $[0, 1]$ and gives $\text{HGR}(Y,S)=0$ iff $Y \perp S$
and 1 if there is a deterministic function to map between them.
Results can be found in figure~\ref{fig:multi-s}.\\

@@

% \newpage
\begin{figure*}[tb]
  \centering
  \subfloat[Original images.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{paper2/Images/celeba/vae_x_original.png}}%
      \label{fig:cvae_celeba_original_x}
  }
  \hfill
  \subfloat[$\bm{x}_u$ null-samples generated by the cVAE model.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{paper2/Images/celeba/vae_recon_y.png}}%
      \label{fig:cvae_celeba_recon_y}
  }
  \hfill
  \subfloat[$\bm{x}_b$ null-samples generated by the cVAE model.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{paper2/Images/celeba/vae_recon_s.png}}%
      \label{fig:cvae_celeba_recon_s}
  }
  \caption{
    CelebA null-samples learned by our cVAE model, with gender as the sensitive attribute.
    (a) The original, untransformed samples from the CelebA dataset
    (b) Reconstructions using only information unrelated to $s$.
    (c) Reconstruction using only information related to $\neg s$.
    The model learns to disentangle gender from the non-gender related information. Compared with the cFlow model, there is a severe degradation in reconstruction quality due to the model trying to simultaneously satisfy conflicting objectives.
    % Attributes such as \emph{makeup} and \emph{hair length} are also often modified in the process due to inherent correlations between them and the sensitive attribute, which the intepretability of our representations allows us to easily identify.
  }\label{fig:celeba_vae}
\end{figure*}

\begin{figure*}[tb]
  \centering
  \subfloat[Original images.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{paper2/Images/celeba/cflow_original_x_suppmat.png}}%
      \label{fig:cflow_celeba_original_x_suppmat}
  }
  \hfill
  \subfloat[$\bm{x}_u$ null-samples generated by the cFlow model.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{paper2/Images/celeba/cflow_xd_suppmat.png}}%
      \label{fig:cflow_celeba_recon_y_suppmt}
  }
  \hfill
  \subfloat[$\mathbf{x}_b$ null-samples generated by the cFlow model.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{paper2/Images/celeba/cflow_xb_suppmat.png}}%
      \label{fig:cflow_celeba_recon_s_suppmat}
  }
  \caption{
    CelebA null-samples learned by our cFlow model, with gender as the sensitive attribute.
    (a) The original, untransformed samples from the CelebA dataset
    (b) Reconstructions using only information unrelated to $s$.
    (c) Reconstruction using only information related to $\neg s$.
    The model learns to disentangle gender from the non-gender related information.
    Attributes such as \emph{makeup} and \emph{hair length} are also often modified in the process (prime examples framed with red) due to inherent correlations between them and the sensitive attribute, which the interpretability of our representations allows us to easily identify.
  }\label{fig:celeba_cflow_suppmat}
\end{figure*}

@@

The results for the range of $\sigma$ values are shown in fig.~\ref{fig:cmnist-transfer}. Unsurprisingly, the performance of both models suffers when the representative and test sets do not completely correspond. However, the cFlow model consistently outperforms the cVAE model, with the gap increasing as the bias decreases.
Although some colour information is retained in the cFlow null-samples, symptomatic of an imperfect transfer, semantic information is almost entirely retained as well.
Conversely, the cVAE is very much flawed in this respect; as can be seen in the bottom row of fig.~\ref{fig:cmnist-transfer}, for some samples, semantic information is degraded to the point of the digit's identity being altered. As a result of this semantic degradation, the performance of the downstream classifier is curtailed by the noisiness of the digit's identity and is relatively unchanging across $\sigma$-values, in contrast to the monotonic improvement of that achieved on the cFlow null-samples.
% \begin{figure}
%   \includegraphics[width=0.6\textwidth]{paper2/Figures/nosinn_cmnist_transfer.pdf}
%   \caption{
%      Results for transfer learning experiments on cMNIST.
%   }%
%   \label{fig:cmnist-transfer}
% \end{figure}

\begin{figure*}[htb]
  \centering
  \subfloat[Performance on cMNIST test data after pre-training on the mixed NIST dataset.]{
      \scalebox{0.6}{\includegraphics[width=\textwidth]{paper2/Figures/nosinn_cmnist_transfer.pdf}} \label{fig:cmnist-transfer}
  }
  %---
  \vspace{10pt}

  \subfloat[Test data input to the cFlow model.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{paper2/Images/cmnist/cflow_tl_original.png}}%
      \label{fig:cflow_tl_original}
  }
  ~~~
%   \hfill
  \subfloat[$\bm{x}_u$ null-samples generated by the cFlow model.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{paper2/Images/cmnist/cflow_tl_xd.png}}%
      \label{fig:cflow_tl_xd}
  }

    \subfloat[Test data input to the cVAE model.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{paper2/Images/cmnist/cvae_tl_original.png}}%
      \label{fig:cvae_tl_original}
  }
  ~~~
%   \hfill
  \subfloat[$\bm{x}_u$ null-samples generated by the cVAE model.]{%
      \scalebox{0.3}{\includegraphics[width=\textwidth]{paper2/Images/cmnist/cvae_tl_xd.png}}%
      \label{fig:cvae_tl_xd}
  }
  \caption{
    Results for the transfer learning experiments in which the representative set consists of colourised samples from EMNIST, KMNIST, and FashionMNIST, while the downstream dataset remains as cMNIST. (a) Quantitative results for different $\sigma$-values. (b-c) Qualitative results for the cFlow model.
    (d-e) Qualitative results for the cVAE model. The qualitative results provide comparisons of the images before (left) and after (right) null-sampling. Note that for some of the cVAE samples, the clarity of the digits has clearly changed due to null-sampling, serving as an explanation for the non-increasing downstream performance.
  }%
  \label{fig:cmnist-transfer-all}
